Crunching Large Graphs with Commodity Processors

### 2011-01-26 doc/hotpar2011/softxmt-hotpar2011.tex

This paper describes the vision of our system and explores the
feasibility of our ideas using a single-node implementation of a
lightweight threading runtime. We use prefetch instructions together
with lightweight threads to tolerate the latency of DRAM access on the
local node node. We use adversarial pointer chasing benchmarks to
verify our runtime's overhead is acceptable. We also model the effects
of pointer chasing on a remote node by artificially increasing
latenciess to the order of several micro-seconds.

The rest of the paper is organized as follows. We quickly describe our
programming model in section~\ref{sec:model}. We describe the
implementation of our latency-tolerant runtime and plans for extending
to multiple nodes in section~\ref{sec:approach}. We evaluate our
runtime in section~\ref{sec:evaluation}.  We present related work in
section~\ref{sec:related} and conclude in
section~\ref{sec:conclusion}.

>>>>

This paper describes the vision of our system and explores the
feasibility of our ideas using a single-node implementation of a
lightweight threading runtime. We use prefetch instructions together
with lightweight threads to tolerate the latency of DRAM access on the
local node. We use worst-case pointer chasing benchmarks to
verify our runtime's overhead is acceptable. We also model the effects
of pointer chasing on a remote node by artificially increasing
latencies to several micro-seconds.

The rest of the paper is organized as follows. We briefly describe our
programming model in section~\ref{sec:model}. We describe the
implementation of our latency-tolerant runtime and plans for extending
to multiple nodes in section~\ref{sec:approach}. We evaluate our
runtime in section~\ref{sec:evaluation}.  We present related work in
section~\ref{sec:related} and conclude in
section~\ref{sec:conclusion}.
